---
title: "Code for the paper 'Analysing kinematic data from recreational runners using functional data analysis'"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Repository Structure:

* :open_file_folder: **code**
  * :open_file_folder: **analysis** -- scripts used to perform the data analysis.
    * :page_facing_up: [01 - Exploratory Plot for Introduction](code/analysis/BFMM-paper-basis-transformation.R)
    * :page_facing_up: [02 - Basis Transformation](code/analysis/BFMM-paper-basis-transformation.R)
    * :page_facing_up: [03 - Model Fitting](code/analysis/BFMM-paper-modelling.R)
    * :page_facing_up: [04 - Bootstrap and Wald Inference](code/analysis/BFMM-paper-bootstrap.R)
    * :page_facing_up: [05 - Plotting Fixed-Effects Results](code/analysis/BFMM-paper-fixef-results.R)
    * :page_facing_up: [06 - Plotting Random-Effects Results](code/analysis/BFMM-paper-covariance-results.R)
    * :page_facing_up: [07 - Additional Exploratory Analysis of Random-Effects Results](code/analysis/BFMM-paper-covariance-extra.R)
    * :page_facing_up: [08 - Analysis of ICC](code/analysis/BFMM-icc-analysis.R)
  * :open_file_folder: **functions** -- custom functions used to perform the data analysis and simulation
    * :page_facing_up: [Custom `ggplot2` theme for figures](code/functions/theme_gunning.R)
    * :page_facing_up: [Functions to help storage and manipulation of `fda::fd` objects](code/functions/functions-helper-smoothing.R)
    * :page_facing_up: [Function to calculate uncentered FPCA scores](code/functions/function-project-mean-onto-fpcs.R)
    * :page_facing_up: [Function to calculate unstructured covariance estimates (based off the `denseFLMM` package)](code/functions/functions-unstructured-covariance.R)
    * :page_facing_up: :page_facing_up: :page_facing_up: :page_facing_up: Tests for the unstructured covariance estimator [(1)](code/functions/cov_unstruct_test-01.R) [(2)](code/functions/cov_unstruct_test-02.R) [(3)](code/functions/cov_unstruct_test-03.R) [(4)](code/functions/cov_unstruct_test-04.R)
    * :page_facing_up: [Function to extract an estimated heteroscedastic residual covariance matrix from an `nlme` object](code/functions/function-get-residual-covariance-matrix.R)
    * :page_facing_up: [Function to calculate Monte Carlo Standard Errors (SEs) for Coverage](code/functions/binomial_se.R)
    * :page_facing_up: [Tests Monte Carlo SEs for Coverage](code/functions/binomial_se_tests.R)
  * :open_file_folder: **simulation** -- scripts to generate and perform the short simulation in the paper
     *  :page_facing_up: [01 - Fit a simple model and generate empirical parameters](code/simulation/BFMM-paper-get-simulation-parameters.R)
     * :page_facing_up: [02 - Generate Eigenfunctions for the Simulation](code/simulation/BFMM-paper-generate-efuns-simulation.R)
     * :page_facing_up: [03 - Functions to Generate Data](code/simulation/BFMM-paper-generate-simulated-data.R)
     * :page_facing_up: [04 - Code to Run and Save Simulation](code/simulation/BFMM-paper-tidied-simulation.R)
     * :page_facing_up: [05 - Assess Estimation and Plot Results](code/simulation/BFMM-paper-simulation-result-plot.R)
     * :page_facing_up: [06 - Assess Coverage and Tabulate Results](code/simulation/BFMM-paper-simulation-coverage-tables.R)

## Timing Results:

```{r, echo = FALSE}
results_path <- here::here("outputs", "results")
boot_time <- readRDS(file = file.path(results_path, "bootstrap-results.rds"))$boot_time
boot_time_mins <- round(boot_time["elapsed"] / 60, 2)
n_cores_used <- readRDS(file = file.path(results_path, "bootstrap-results.rds"))$n_cores_used
B <- readRDS(file = file.path(results_path, "bootstrap-results.rds"))$B
date <- readRDS(file = file.path(results_path, "bootstrap-results.rds"))$date
```

It took **`r boot_time_mins` minutes** to run the bootstrap analysis using **`r B` bootstrap replicates** with computing shared across **`r n_cores_used` cores** on a 2019 MacBook Pro with a 2.4 GHz Quad-Core Intel Core i5 processer and 8 GB of memory (code ran on `r date`).

## Reproducibility

```{r, echo=FALSE}
 readRDS(file = file.path(results_path, "bootstrap-results.rds"))$sessionInfo
```

We have stored `.Random.seed` on each iteration of the simulation in a list called `simulation_seeds`. The seed can be set to produce any iteration by using the command (described [here](https://stackoverflow.com/questions/19614314/can-i-get-seed-somehow)):

```{r, eval = FALSE}
# to set seed as it was on iteration i
given_seed <- simulation_seeds[[i]]
.Random.seed <- given_seed
```




